---
title: "Movie Research"
author: "Muthia"
date: "8/18/2020"
output: html_document
---
This script performs the following steps:
Step 1: Step 1: Install packages, load required library packages, and set working directories
Step 2: Retrieving Data
Step 3: Data Pre-processing (R)
Step 4: EDA


Step 1: Install packages, load required library packages, and set working directories

library(ggplot2)                       
library(data.table)
library(reshape2)
library(recommenderlab)
library(tidytext)
library(textclean)
library(wordcloud)
library(tidyr)
library(dplyr)
library(stringr)
library(tidyverse)
library(stopwords)
library(readxl)
library(tm)
library(devtools)
library(data.table)
library(sqldf)
library(plotly)
library(recommenderlab)
library(ggthemes)
library(gridExtra)
library(grid)
library(lattice)

Step 2: Retrieving Data (IMDB)


```{r}
IMDB_Movies <- read.csv("C:/Users/Aulia Muthia/Downloads/Riset Mandiri/IMDB-Dataset/IMDB movies.csv", stringsAsFactors=FALSE)
IMDB_Ratings <- read.csv("C:/Users/Aulia Muthia/Downloads/Riset Mandiri/IMDB-Dataset/IMDB ratings.csv", stringsAsFactors=FALSE)
IMDB_Movies
IMDB_Ratings
```

Step 3 : Data Pre-processing (IMDB)

```{r}
IMDB_Movies_Genre <- as.data.frame(IMDB_Movies$genre, stringsAsFactors = FALSE)
IMDB_Movies_Genre

IMDB_Movies_Genre2 <- as.data.frame(tstrsplit(IMDB_Movies_Genre[,1], 
                                              '[,]', 
                                              type.convert=TRUE), 
                                    stringsAsFactors=FALSE) #DataFlair
colnames (IMDB_Movies_Genre2) <- c("genre1", "genre2", "genre3")
IMDB_Movies_Genre2

IMDB_Movies1 <- cbind(IMDB_Movies[], IMDB_Movies_Genre2[])
head(IMDB_Movies1)
```

Step 4: EDA
   
  1. Types of genre on IMDB 
```{r}
IMDB_Movies_Genre <- data.frame(IMDB_Movies1$genre,
                                         IMDB_Movies1$genre1,
                                         IMDB_Movies1$genre2,
                                         IMDB_Movies1$genre3)

colnames(IMDB_Movies_Genre) <- c("Genre", "Genre1", "Genre2", "Genre3")

head(IMDB_Movies_Genre)

genre1_plot = 
  genre1_n %>% 
  mutate (genre1 = fct_reorder(genre1,n)) %>%
  ggplot(aes(x=genre1,y=n,fill=n)) + 
  geom_col(position = "stack") +
  labs (x="Genre 1",
        title = "Percentage of Genre 1 Type on IMDB",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia") + 
  #flip x to y and y to x 
  coord_flip() +
  theme_clean() +
  theme (
    legend.position = "left",
    axis.text.x = element_text(angle=90,hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  ) 
genre1_plot

genre2_plot = 
  genre2_n %>% 
  drop_na() %>%
  mutate (genre2 = fct_reorder(genre2,n)) %>%
  ggplot(aes(x=genre2,y=n,fill=n)) + 
  geom_col(position = "stack") +
  labs (x="Genre 2",
        title = "Percentage of Genre 2 Type on IMDB",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia") + 
  #flip x to y and y to x 
  coord_flip() +
  theme_clean() +
  theme (
    legend.position = "left",
    axis.text.x = element_text(angle=90,hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  ) 
genre2_plot

genre3_plot = 
  genre3_n %>% 
  drop_na() %>%
  mutate (genre3 = fct_reorder(genre3,n)) %>%
  ggplot(aes(x=genre3,y=n,fill=n)) + 
  geom_col(position = "stack") +
  labs (x="Genre 3",
        title = "Percentage of Genre 3 Type on IMDB",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia") + 
  #flip x to y and y to x 
  coord_flip() +
  theme_clean() +
  theme (
    legend.position = "left",
    axis.text.x = element_text(angle=90,hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  ) 
genre3_plot

grid.arrange(genre1_plot,genre2_plot,genre3_plot, ncol = 3)

```
  
  2. Average movie rating distribution
  
```{r}
IMDB_Ratings %>% ggplot(aes(x=weighted_average_vote)) +  
  geom_histogram(binwidth = 1, fill="seagreen") +
  geom_freqpoly(binwidth = 1, col="hotpink") +
  labs (x="Weighted Average Vote",
        y="Count of Weighted Average Rate",
        title = "Distribution of Weighted Average Rate",
        subtitle = "IMDB Ratings",
        caption = "Developed by : Aulia Muthia") + 
  theme_clean() +
  theme (
    legend.position = "left",
    axis.text.x = element_text(hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  ) 

```
  
  
  3. Number of ratings per movie
  
```{r}
IMDB_Movies %>% ggplot(aes(x = votes)) +
  geom_histogram(bins = 10) + 
  ggtitle('Histogram of Movie Ratings') 
  geom_histogram(fill="seagreen", bins = 10000) +
  labs (x="Number of Ratings per Movie",
        y="Movies",
        title = "Number of Ratings per Movie",
        subtitle = "IMDB Ratings",
        caption = "Developed by : Aulia Muthia") + 
  theme_clean() +
  theme (
    legend.position = "left",
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  )
```
  
  
  4. Heat map genre 1 genre 2 based on vote
  
```{r}
ggplot(IMDB_Movies1, aes(genre2,genre1, fill= avg_vote)) + 
  geom_tile() +
  labs (x = "Genre 2",
        y = "Genre 1",
        title = "Genre 1 & 2 Type and Rate on IMDB",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia")+
  scale_fill_gradient(low="white", high="black") +
   theme_clean() +
    theme (
    legend.position = "left",
    axis.text.x = element_text(angle=90,hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  ) 
```
  
  5. genre + year and avg vote

```{r}
IMDB_Movies1 %>%
  filter(year>=2000) %>%
  ggplot(aes(year,genre1, fill= avg_vote)) + 
  geom_tile() +
  labs (x = "Year",
        y = "Genre",
        title = "Genre Type and Year by Rate on IMDB",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia")+
  scale_fill_gradient(low="white", high="black") +
   theme_clean() +
    theme (
    legend.position = "left",
    axis.text.x = element_text(hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  )
```
  
  6. top 10 movies based on votes
  
```{r}
Top_10_Rated_Movies <- sqldf("SELECT title,  genre, avg_vote, votes
                              FROM IMDB_Movies1
                              ORDER BY votes DESC
                             LIMIT 10")


Top_10_Rated_Movies %>% 
  mutate (title = fct_reorder(title,votes)) %>%
  ggplot(aes(x=title,y=votes)) + 
  geom_bar(stat="identity", colour = "black") +
  labs (x = "Movie Title",
        y = "Total Votes",
        title = "Top 10 Movies on IMDB 
    by Number of Votes",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia") + 
  geom_text(aes(label=votes), hjust=-0.1, size=3) +
  #flip x to y and y to x 
  coord_flip() +
  theme_clean() +
  theme (
    legend.position = "left",
    axis.text.x = element_text(angle=90,hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  ) 
```
  
7. top 10 movies based on rate 
 
```{r}
Top_10_Best_Vote_Movies <- sqldf("SELECT title,  genre, weighted_average_vote, votes
                              FROM Movie_Ratings
                              ORDER BY weighted_average_vote DESC
                             LIMIT 10")


Top_10_Best_Vote_Movies %>% 
  mutate (title = fct_reorder(title,weighted_average_vote)) %>%
  ggplot(aes(x=title,y=weighted_average_vote)) + 
  geom_bar(stat="identity", fill="blue") +
  labs (x = "Movie Title",
        y = "Rating",
        title = "Top 10 Movies on IMDB by Rating",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia") + 
        geom_text(aes(label=weighted_average_vote), hjust=-0.1, size=3) +
  #flip x to y and y to x 
  coord_flip() +
  theme_clean() +
  theme (
    legend.position = "left",
    axis.text.x = element_text(hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  ) 
```
 
  8. rate per country 
  
```{r}

IMDB_Movies_Country <- as.data.frame(Movie_Ratings$country, stringsAsFactors = FALSE)
IMDB_Movies_Country

IMDB_Movies_Country <- as.data.frame(tstrsplit(IMDB_Movies_Country[,1], 
                                              '[,]', 
                                              type.convert=TRUE), 
                                              stringsAsFactors=FALSE) #DataFlair

colnames (IMDB_Movies_Country) <- c("Country1", "Country2")
IMDB_Movies_Country

IMDB_Movies_Country <- IMDB_Movies_Country %>%
  select(Country1, Country2)

IMDB_Movies_Country <- cbind(IMDB_Movies[], IMDB_Movies_Country[])
head(IMDB_Movies_Country)

IMDB_Movies_Country1 <- sqldf("SELECT avg(avg_vote) as average_vote, Country1 as Country
      FROM IMDB_Movies_Country
      GROUP BY Country
      ORDER BY average_vote DESC
      LIMIT 10") 

IMDB_Movies_Country1 %>% 
  mutate (Country = fct_reorder(Country,average_vote)) %>%
    ggplot(aes(x=Country,y=average_vote,color=average_vote)) + 
  geom_point(stat="identity") +
  scale_color_gradient(low="blue", high="red") +
  labs (x = "Country",
        y = "Rating",
        title = "Top 10 Country on IMDB by Rating",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia") + 
  #flip x to y and y to x 
  coord_flip() +
  theme_clean() +
  theme (
    axis.text.x = element_text(hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  )
```
 
 
  9. correlation #vote and rate
  
```{r}
# Find the Correlation Between Number of Votes and Average Vote

IMDB_Movies1 %>%
  ggplot(aes(y = avg_vote, x = votes,color=votes)) +  
  geom_point() + 
  scale_color_gradient(low="blue", high="red") +
  scale_x_log10() +
  geom_smooth(method = "lm", se = FALSE) +
  labs (x = "Log Number of Vote",
        y = "Rate",
        title = "Correlation Number of Vote and Rate",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia") + 
  theme_clean() +
  theme (
    axis.text.x = element_text(hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  )

# Find the Correlation Coefficient

cor(IMDB_Movies1$votes, 
    IMDB_Movies1$avg_vote)
```
  
  10. wordcloud all description

```{r}
#Convert IMDB_Movies$description to vector from dataframe
IMDB_Movies_Description <- as.vector(IMDB_Movies$description,mode="any")
is.vector(IMDB_Movies_Description)

head(IMDB_Movies_Description)

IMDB_Movies_Description %>% 
  str_to_lower() %>% # a function from stringr package to convert characters to lowercase 
  replace_contraction() %>% # replace contraction with both words
  replace_word_elongation() %>% # replace word elongation with shortened form
  strip() %>% #remove all non words character
  head(10)

#Tokenize & Remove Stoprwords

stopwords <- read.csv('C:/Users/Aulia Muthia/Downloads/SEMESTER 8/SIP/stopwords/stopwords.csv')

IMDB_Movies_Description_Words <- enframe(IMDB_Movies_Description,value = "description", name = NULL) %>% 
                        #to convert dataframe to vector
                        unnest_tokens(description,description) %>% 
                        #tokenization to transform all the words from text to one data
                        count(description,sort=T) %>% 
                        anti_join(stopwords,by = c("description"="stopwords")) #remove stopwords
                        #stopwords are words that do not have any additional meaning to the core concept words

head(IMDB_Movies_Description_Words,20)

#Create Wordcloud with wordcloud package in R

IMDB_Movies_Description_Words%>% #recall the data that we will used
  with(
    wordcloud(
      words = description, #column within our data that we want to visualize
      freq = n, #column within our data that contains frequency of words
      max.words = 100, #count of words limit that we want to visualize in wordcloud 
      random.order = FALSE, #to visualize the data based on the frequency
      colors = brewer.pal (name = "Dark2", 6) #color palette
    )
  )

```
  
  11. wordcloud 18 yr old based on rate >7
  
```{r}
#18 yr old all gender

Movie_Ratings_18 <- Movie_Ratings %>% 
                  select(description, allgenders_18age_avg_vote, allgenders_18age_votes) %>%
                  filter(allgenders_18age_avg_vote > 7)

IMDB_Movies_Description_18 <- as.vector(Movie_Ratings_18$description,mode="any")
is.vector(IMDB_Movies_Description_18)

head(IMDB_Movies_Description_18)

IMDB_Movies_Description_18 %>% 
  str_to_lower() %>% # a function from stringr package to convert characters to lowercase 
  replace_contraction() %>% # replace contraction with both words
  replace_word_elongation() %>% # replace word elongation with shortened form
  strip() %>% #remove all non words character
  head(30)

IMDB_Movies_Description_Words_18 <- 
                        enframe(IMDB_Movies_Description_18,value = "description", name = NULL) %>% 
                        #to convert dataframe to vector
                        unnest_tokens(description,description) %>% 
                        #tokenization to transform all the words from text to one data
                        count(description, sort=TRUE) %>% 
                        anti_join(stopwords,by = c("description"="stopwords")) #remove stopwords
                        #stopwords are words that do not have any additional meaning to the core concept words

head(IMDB_Movies_Description_Words_18,20)

#Create Wordcloud with wordcloud package in R

IMDB_Movies_Description_Words_18%>% #recall the data that we will used
  with(
    wordcloud(
      words = description, #column within our data that we want to visualize
      freq = n, #column within our data that contains frequency of words
      max.words = 100, #count of words limit that we want to visualize in wordcloud 
      random.order = FALSE, #to visualize the data based on the frequency
      colors = brewer.pal (name = "Dark2", 6) #color palette
    )
  )

```
  
  12. wordcloud 30 yr old based on rate >7
  
```{r}
#30 yr old all gender

Movie_Ratings_30 <- Movie_Ratings %>% 
                  select(description, allgenders_30age_avg_vote, allgenders_30age_votes) %>%
                  filter(allgenders_30age_avg_vote > 7)

#Convert IMDB_Movies$description to vector from dataframe
IMDB_Movies_Description_30 <- as.vector(Movie_Ratings_30$description,mode="any")
is.vector(IMDB_Movies_Description_30)

head(IMDB_Movies_Description_30,6)

IMDB_Movies_Description_30 %>% 
  str_to_lower() %>% # a function from stringr package to convert characters to lowercase 
  replace_contraction() %>% # replace contraction with both words
  replace_word_elongation() %>% # replace word elongation with shortened form
  strip() %>% #remove all non words character
  head(30)

#Tokenize & Remove Stoprwords

stopwords <- read.csv('C:/Users/Aulia Muthia/Downloads/SEMESTER 8/SIP/stopwords/stopwords.csv')

IMDB_Movies_Description_Words_30 <- enframe(IMDB_Movies_Description_30,value = "description", name = NULL) %>% 
                        #to convert dataframe to vector
                        unnest_tokens(description,description) %>% 
                        #tokenization to transform all the words from text to one data
                        count(description,sort=TRUE) %>% 
                        anti_join(stopwords,by = c("description"="stopwords")) #remove stopwords
                        #stopwords are words that do not have any additional meaning to the core concept words

head(IMDB_Movies_Description_Words_30,20)

#Create Wordcloud with wordcloud package in R

IMDB_Movies_Description_Words_30%>% #recall the data that we will used
  with(
    wordcloud(
      words = description, #column within our data that we want to visualize
      freq = n, #column within our data that contains frequency of words
      max.words = 100, #count of words limit that we want to visualize in wordcloud 
      random.order = FALSE, #to visualize the data based on the frequency
      colors = brewer.pal (name = "Dark2", 6) #color palette
    )
  )

```

  13. wordcloud 45 yr old based on rate >7

```{r}
#45 yr old all gender

Movie_Ratings_45 <- Movie_Ratings %>% 
                  select(description, allgenders_45age_avg_vote, allgenders_45age_votes) %>%
                  filter(allgenders_45age_avg_vote > 7)

#Convert IMDB_Movies$description to vector from dataframe
IMDB_Movies_Description_45 <- as.vector(Movie_Ratings_45$description,mode="any")
is.vector(IMDB_Movies_Description_45)

head(IMDB_Movies_Description_45,6)

IMDB_Movies_Description_45 %>% 
  str_to_lower() %>% # a function from stringr package to convert characters to lowercase 
  replace_contraction() %>% # replace contraction with both words
  replace_word_elongation() %>% # replace word elongation with shortened form
  strip() %>% #remove all non words character
  head(30)

#Tokenize & Remove Stoprwords

stopwords <- read.csv('C:/Users/Aulia Muthia/Downloads/SEMESTER 8/SIP/stopwords/stopwords.csv')

IMDB_Movies_Description_Words_45 <- enframe(IMDB_Movies_Description_45,value = "description", name = NULL) %>% 
                        #to convert dataframe to vector
                        unnest_tokens(description,description) %>% 
                        #tokenization to transform all the words from text to one data
                        count(description,sort=TRUE) %>% 
                        anti_join(stopwords,by = c("description"="stopwords")) #remove stopwords
                        #stopwords are words that do not have any additional meaning to the core concept words

head(IMDB_Movies_Description_Words_45,20)

#Create Wordcloud with wordcloud package in R

IMDB_Movies_Description_Words_45%>% #recall the data that we will used
  with(
    wordcloud(
      words = description, #column within our data that we want to visualize
      freq = n, #column within our data that contains frequency of words
      max.words = 100, #count of words limit that we want to visualize in wordcloud 
      random.order = FALSE, #to visualize the data based on the frequency
      colors = brewer.pal (name = "Dark2", 6) #color palette
    )
  )
```


  14. join data

```{r}
# Join IMDB_Movies and IMDB_Ratings based on Movie ID


Movie_Ratings = IMDB_Movies1 %>% 
  left_join(IMDB_Ratings, by = 'imdb_title_id') 

head(Movie_Ratings,10)

Movie_Ratings %>% ggplot(aes(genre1,allgenders_18age_votes, fill= allgenders_18age_avg_vote)) + 
  geom_tile() +
  labs (x = "Genre 2",
        y = "Genre 1",
        title = "Heat Map of Genre 1 & 2 Type on IMDB",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia")+
  scale_fill_gradient(low="white", high="black") +
   theme_clean() +
    theme (
    legend.position = "left",
    axis.text.x = element_text(angle=90,hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  ) 


```
  
    15. genre preferences based on ages 

```{r}
Movie_Genre_18 <- Movie_Ratings %>% 
                  select(genre1, allgenders_18age_avg_vote, allgenders_18age_votes) %>%
                  filter(allgenders_18age_avg_vote > 7) %>%
  ggplot(aes(genre1,allgenders_18age_avg_vote, fill= allgenders_18age_votes)) + 
  geom_tile() +
  labs (x = "Genre",
        y = "Rate by 18 Years Old",
        title = "Genre and Rate by 18 yr Old User on IMDB",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia")+
  scale_fill_gradient(low="white", high="black") +
   theme_clean() +
    theme (
    legend.position = "left",
    axis.text.x = element_text(angle=90,hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  ) 

Movie_Genre_30 <- Movie_Ratings %>% 
                  select(genre1, allgenders_30age_avg_vote, allgenders_30age_votes) %>%
                  filter(allgenders_30age_avg_vote > 7) %>%
  ggplot(aes(genre1,allgenders_30age_avg_vote, fill= allgenders_30age_votes)) + 
  geom_tile() +
  labs (x = "Genre",
        y = "Rate by 30 Years Old",
        title = "Genre and Rate by 30 yr Old User on IMDB",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia")+
  scale_fill_gradient(low="white", high="black") +
   theme_clean() +
    theme (
    legend.position = "left",
    axis.text.x = element_text(angle=90,hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  ) 

Movie_Genre_45 <- Movie_Ratings %>% 
                  select(genre1, allgenders_45age_avg_vote, allgenders_45age_votes) %>%
                  filter(allgenders_45age_avg_vote > 7) %>%
  ggplot(aes(genre1,allgenders_45age_avg_vote, fill= allgenders_45age_votes)) + 
  geom_tile() +
  labs (x = "Genre",
        y = "Rate by 45 Years Old",
        title = "Genre and Rate by 45 yr Old User on IMDB",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia")+
  scale_fill_gradient(low="white", high="black") +
   theme_clean() +
    theme (
    legend.position = "left",
    axis.text.x = element_text(angle=90,hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  ) 
   
Movie_Genre_18
Movie_Genre_30
Movie_Genre_45
               
```

  
16. move genre based on rate
```{r}
ggplot(data = IMDB_Movies1) + 
  geom_histogram(binwidth =1, aes(x = avg_vote, fill = genre1), colour = "black") +
  labs (x = "Rate",
        y = "Count",
        title = "Movie Genre Based on Rate",
        subtitle = "IMDB Data",
        caption = "Developed by : Aulia Muthia")+
   theme_clean() +
    theme (
    legend.position = "left",
    axis.text.x = element_text(hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  ) 
```

